### 2024-11-06 paper.qmd
stage 1 ready

<!--- TABLE 2 HERE --->
[**Table 2**]{#tbl-sample-characteristics}. Sample characteristics from which, continuous RRi monitoring data was collected during a rest-exercise-rest protocol.

@@

[**Figure 5**]{#fig-2d-kernel-density}. Upper panel shows the mean and standard deviation (SD) from each of the subject's RRi recordings, used for the standardization process. Lower panel indicate the 2D kernel density of standardized RRi dynamics over time from a sample of individuals subjected to a rest-exercise-rest protocol. Darker colors indicate greater probability density. The contrary can be said about lighter colors.

>>>>

|Characteristic |Overall        |Female         |Male           |
|:--------------|:--------------|:--------------|:--------------|
|Sex            |—              |217 (79.8%)    |55 (20.2%)     |
|Age            |71.14 ± 6.03   |70.73 ± 6.27   |72.73 ± 4.7    |
|SBP (mm hg)    |130.23 ± 17.07 |129.58 ± 17.37 |132.8 ± 15.69  |
|DBP (mm hg)    |77.1 ± 9.58    |76.68 ± 9.83   |78.75 ± 8.4    |
|MAP (mm hg)    |94.81 ± 10.69  |94.31 ± 10.95  |96.76 ± 9.45   |
|PP (mm hg)     |53.14 ± 14.07  |52.9 ± 14.26   |54.05 ± 13.38  |
|BMI            |30.66 ± 5.43   |30.7 ± 5.64    |30.53 ± 4.53   |
|Weight (kg)    |75.06 ± 14.23  |73.88 ± 14.09  |79.69 ± 13.95  |
|Height (cm)    |156.56 ± 9.18  |155.29 ± 8.46  |161.55 ± 10.24 |

[**Table 2**]{#tbl-sample-characteristics}. Sample characteristics from which, continuous RRi monitoring data was collected during a rest-exercise-rest protocol. Data is presented as Mean ± SD.

@@

[**Figure 5**]{#fig-2d-kernel-density}. Left panel shows the mean and standard deviation (SD) from each of the subject's RRi recordings, used for the standardization process. Right panel indicate the 2D kernel density of standardized RRi dynamics over time from a sample of individuals subjected to a rest-exercise-rest protocol. Darker colors indicate greater probability density. The contrary can be said about lighter colors.

### Individual-level estimates
